Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-09 Paper/paper-draft-Padgett-Thiam.Rmd
Update paper-draft-Padgett-Thiam.Rmd

>>>>

 Kearney, M. W. (2018). rtweet: Collecting Twitter Data. R package version 0.6.7 
 Retrieved from https://cran.r-project.org/package=rtweet

 Silge J, Robinson D (2016). “tidytext: Text Mining and Analysis Using Tidy Data Principles in R.” _JOSS_, *1*(3). 
 doi: 10.21105/joss.00037 (URL http://doi.org/10.21105/joss.00037), <URL:http://dx.doi.org/10.21105/joss.00037>.

 D. Kahle and H. Wickham. ggmap: Spatial Visualization with ggplot2.
 The R Journal, 5(1), 144-161. URL http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf

 Garrett Grolemund, Hadley Wickham (2011). Dates and Times Made Easy with
 lubridate. Journal of Statistical Software, 40(3), 1-25. URL http://www.jstatsoft.org/v40/i03/.

 Benoit K, Watanabe K, Wang H, Nulty P, Obeng A, Müller S, Matsuo A (2018).  “quanteda: An R package for the quantitative
 analysis of textual data.” _Journal of Open Source Software_, *3*(30), 774. doi: 10.21105/joss.00774 
 (URL: http://doi.org/10.21105/joss.00774), <URL: https://quanteda.io>.

  Stefan Feuerriegel and Nicolas Proellochs (2019). SentimentAnalysis: Dictionary-Based Sentiment Analysis. 
  R package version 1.3-3. https://CRAN.R-project.org/package=SentimentAnalysis

  Barret Schloerke, Jason Crowley, Di Cook, Francois Briatte, Moritz Marbach, Edwin Thoen, 
  Amos Elberg and Joseph Larmarange (2018). GGally:  Extension to 'ggplot2'. R package version 1.4.0. 
  https://CRAN.R-project.org/package=GGally

   H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York, 2016.

  Gergely Daróczi and Roman Tsegelskyi (2018). pander: An R 'Pandoc'  Writer. R package version 0.6.3.
  https://CRAN.R-project.org/package=pander
